Classifier

### 2019-03-01 Paper/paper.Rmd
Knitted the current version of the 01 file

---
title: "Classifier"
output: github_document
---

# Overview
In this R Markdown, we'll be documenting how we built our model for classifying tweets as "complaints" and "non-complaints." The code is almost entirely derived from the Code/cnn-classifier/R/fasttext_supervised_classifier.R script.

# Load Packages
```{r}
# library(fastrtext)
# library(tidyverse)
```

# Define Functions
No functions have been defined in this file.

# About fastText
fastText was designed by Facebook and it allows us to build models for both classification and word embeddings. Classification refers to analyzing a set of text, and labeling it according to the topics it closely relates to. Word embeddings help us predict which words are most closely related to a single word of interest.

@@

# Execute Code

## List File Paths of Model and Data
To build our fasttext classification model, we begin by defining where we want to store our fastText model once we've trained it. In our case, we want to store the model in Output/models and name the model class_mod_1.dat. Within R, we'll refer to this file path as file_model.

@@

## Read in the Data
We have our training and test data kept in one csv file. We'll read it in after we've filtered all short tweets (with greater than five characters). We'll name this object tweet_data.
```{r}
# This code (and all code below) is broken because we don't have access to a tweet_sample_5k_full.csv file.

@@

## Format the Training Data
For any supervised learning model (such as complaint classification), our training and test datasets need to have data labeled with the "correct" answers. This will allow our model to "learn" the correct answers, and it will hopefully help our model accurately predict correct answers.

@@

### Create the .txt Files
As mentioned earlier, we need to create a text file of our training and test datasets because the fastText model only takes character vectors as inputs. With our data labeled both for training/test and complaint/non-complaint, we're ready to do this. We will use the write_lines() function to do this. The train_data_path is the file location we specified earlier in this script.

@@

## Train the Model
The package we are using (fastrtext) uses the execute() function to train the model. This function makes more sense if you've followed the fastText tutorials, but put simply, it concotenates the arguments into a single command which is then run in the terminal.

@@

## Review Model:
We'll want to see how a few of the predictions turned out. 
```{r}
# prediction are returned as a list with words and probabilities
# predictions <- predict(model, sentences = test_data_lines, simplify = TRUE, unlock_empty_predictions = TRUE)
# head(predictions, 5)
```

@@

## Accuracy
Let's look at how accurately the model predicted names
```{r}
# # Compute accuracy
# mean(names(unlist(predictions)) == test_labels_without_prefix, na.rm = TRUE)
```

@@

# Analysis

>>>>

---
title: "Classifier"
output: github_document
---
# The Classification Model
A key component to successfuly using twitter data to assess service failures is the ability to classify tweets as complaints and non-complaints. If our team can accurately classify a tweet, we will be capable of tackling the greater issue of judging how serious the complaint is, and whether or not a company needs to take action.

While there are an infinite number of methods to perform this task, our team has identified three tools to aid us in our classification: Principal Component Analysis (PCA), FastText, and XGBoost. Using these three tools, we've created a "frankenstein model" that incorporates all three tools listed above. The model has been trained on 2,500 tweets labeled 0 for "non-complaint" and 1 for "complaint." We have then tested the model on a similarly-sized dataset.

To use our model, we feed a set of tweets into a PCA model and a FastText classification model. The output of these two models is then fed into our XGBoost model, which makes a binary prediction for the tweet as a complaint or non-complaint.

Because our model uses three distinct modeling techniques, I will refer to each of these modeling techniques as "sub-models"

# The FastText Sub-Model
## Overview
In this R Markdown, we'll be documenting how we built our model for classifying tweets as "complaints" and "non-complaints." The code is almost entirely derived from the Code/cnn-classifier/R/fasttext_supervised_classifier.R script.

## Load Packages
```{r}
# library(fastrtext)
# library(tidyverse)
```

## Define Functions
No functions have been defined in this file.

## About fastText
fastText was designed by Facebook and it allows us to build models for both classification and word embeddings. Classification refers to analyzing a set of text, and labeling it according to the topics it closely relates to. Word embeddings help us predict which words are most closely related to a single word of interest.

@@

## Execute Code

### List File Paths of Model and Data
To build our fasttext classification model, we begin by defining where we want to store our fastText model once we've trained it. In our case, we want to store the model in Output/models and name the model class_mod_1.dat. Within R, we'll refer to this file path as file_model.

@@

### Read in the Data
We have our training and test data kept in one csv file. We'll read it in after we've filtered all short tweets (with greater than five characters). We'll name this object tweet_data.
```{r}
# This code (and all code below) is broken because we don't have access to a tweet_sample_5k_full.csv file.

@@

### Format the Training Data
For any supervised learning model (such as complaint classification), our training and test datasets need to have data labeled with the "correct" answers. This will allow our model to "learn" the correct answers, and it will hopefully help our model accurately predict correct answers.

@@

#### Create the .txt Files
As mentioned earlier, we need to create a text file of our training and test datasets because the fastText model only takes character vectors as inputs. With our data labeled both for training/test and complaint/non-complaint, we're ready to do this. We will use the write_lines() function to do this. The train_data_path is the file location we specified earlier in this script.

@@

### Train the Model
The package we are using (fastrtext) uses the execute() function to train the model. This function makes more sense if you've followed the fastText tutorials, but put simply, it concotenates the arguments into a single command which is then run in the terminal.

@@

### Review Model:
We'll want to see how a few of the predictions turned out. 
```{r}
# prediction are returned as a list with words and probabilities
# predictions <- predict(model, sentences = test_data_lines, simplify = TRUE, unlock_empty_predictions = TRUE)
# head(predictions, 5)
```

@@

### Accuracy
Let's look at how accurately the model predicted names
```{r}
# # Compute accuracy
# mean(names(unlist(predictions)) == test_labels_without_prefix, na.rm = TRUE)
```

@@

## Analysis

# The PCA Sub-Model

# The XGBoost Sub-Model

## Intro to XGBoost
XGBoost is a tool that uses gradient-boosted trees for classification. A basic understanding of decision trees and random forests is crucial to understanding gradient-boosting as well as the XGBoost package.

Decision Trees:
Decision trees are models that use a series of binary (yes/no) questions, and classify something based on the answers to those binary questions.

Simple Decision Tree Example:
Is it snowing? If so, it is a good day to ski. If not, it is not a good day to ski.

Random Forests:

Gradient Boosting:

Links:
